---
title: "County Dashboard Comparison"
output:
  pdf_document: default
  html_notebook: default
---
```{r echo = FALSE}
require(tidyverse)
library(psych)
library(ggplot2)
library(car)
library(lme4)
library(emmeans)
library(pwr)
library(patchwork)
library(rstatix)
library(effectsize)
library(GPArotation)
# environment to include the ss_psych450_rws3 platform
load("ss_psych450_rws3")
```

Load Data

```{r}
results <- read.csv("data_clean.csv")

# trust in data is the column: bar-data_6
# trust in vis is the column: bar-vis_6
```

Trust in Vis

```{r}
# results$isCovidData <- factor(results$isCovidData, levels = c(0, 1),
#                   labels = c("Crop Data", "Covid Data"))
````

```{r}

MinMeanSEMMax <- function(x) {
  v <- c(min(x), mean(x) - sd(x)/sqrt(length(x)), mean(x), mean(x) + sd(x)/sqrt(length(x)), max(x))
  names(v) <- c("ymin", "lower", "middle", "upper", "ymax")
  v
}

results %>%
  # group_by(complexity, isCovidData) %>%
  ggplot(aes( x = vis.trust_6, y = 0, cex=1.5, colour = as.factor(isCovidData))) +
  scale_color_manual(values = c("purple", "orange")) +
  ylim(-0.5, 0.5) +
  geom_jitter(data = results, width = 0.3, height = 0.2, color = "light gray", alpha = 0.5) +
  #stat_summary(fun.data=MinMeanSEMMax, geom="boxplot", colour="red") +

  geom_boxplot(lwd = 1, fatten = NULL, width = 0.25, alpha = 0.5) +

  geom_segment(data = results %>% 
                group_by(complexity, isCovidData) %>%
                summarize(n = n(), 
                           mean = mean(vis.trust_6),
            se = sd(data.trust_6)/sqrt(n)), 
              aes(x = mean, xend = mean, y = -.25, yend = .25,  colour = as.factor(isCovidData)), size = 1) +
        # stat_summary(fun.data = "mean_cl_boot", colour = "red", size = 0.5, position = position_nudge(x=0.25, y=0), alpha=0.5) +

  geom_text( data = results %>% 
                group_by(complexity, isCovidData) %>%
                summarize(n = n(), 
                           mean = round(mean(vis.trust_6),digits=2),
            se = round(sd(data.trust_6)/sqrt(n),digits=2),
                          vis.trust_6 = mean(vis.trust_6)),
            # aes(label = paste(mean, "[",mean-se,",",mean+se,"]"), x = 6.2, y = 0.43, fontface = 3), size=3, colour = "black")+
              aes(label = paste(mean), x = mean, y = .35, fontface = 3), size=4, colour = "black")+

  facet_grid(complexity ~ isCovidData) +
  xlab("Trust in Visualization") +
  theme_minimal() + 
  theme(panel.spacing = unit(2, "lines"),
        legend.position = "none",
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank())



ggsave(paste("complexity_dataType_interaction.pdf", sep=""))

```


```{r}
results %>%
  group_by(complexity, isCovidData) %>%
  summarize(n = n(),
            mean = mean(vis.trust_6),
            se = sd(vis.trust_6)/sqrt(n),
            n = n)
```

```{r}
# results$isCovidData <- factor(results$isCovidData, levels = c(0, 1),
#                   labels = c("Crop Data", "Covid Data"))

results %>%
  ggplot(aes(x = data.trust_6, y = 0)) +
  # scale_color_manual(values = c("purple", "orange")) +
  ylim(-0.5, 0.5) +
  geom_jitter(data = results, width = 0.25, height = 0.2, color = "light gray", alpha = 0.5) +
  geom_boxplot(lwd = 1, fatten = NULL, width = 0.25, alpha = 0.5, color = "salmon") +
  # labs(title = "Trust in data") + 
  geom_vline(data = results %>% 
                group_by(complexity) %>%
                summarize(n = n(), 
                          data.trust_6 = mean(data.trust_6)), 
              aes(xintercept = data.trust_6), size = 1,colour = "salmon") +
  geom_text( data = results %>% 
                group_by(complexity) %>%
                summarize(n = n(), 
                           mean = round(mean(data.trust_6),digits=2),
            se = round(sd(data.trust_6)/sqrt(n),digits=2),
                          vis.trust_6 = mean(vis.trust_6)),
            aes(label = paste(mean, "[",mean-se,",",mean+se,"]"), x = 6.8, y = 0.43, fontface = 3), size=3, colour = "black")+
  facet_grid(rows = vars(complexity)) +
  xlab("Trust in Data") +
  theme_minimal() + 
  theme(panel.spacing = unit(2, "lines"),
        legend.position = "none",
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank())

ggsave(paste("complexity_interaction.pdf", sep=""))

```


```{r}
results %>%
  group_by(complexity) %>%
  summarize(n = n(),
            mean = mean(data.trust_6),
            se = sd(data.trust_6)/sqrt(n),
            n = n)
```


```{r}
model <- lm(formula = vis.trust_6 ~ complexity * as.factor(isCovidData) * chartType
                                    + Age + Gender + State_1 + Education + Parents_education + Language + Ethnicity + Income + Religion + trust.in.science_7 + need_for_cognition + interpersonal.trust_1 ,
            data = results)
anova(model)

# post-hoc tests
aov(vis.trust_6 ~ complexity * as.factor(isCovidData), data = results) %>% tukey_hsd()
# effect sizes
eta_squared(aov(vis.trust_6 ~ complexity * as.factor(isCovidData) * chartType + 
                  Age + Gender + State_1 + Education + Parents_education + Language + 
                  Ethnicity + Income + Religion + trust.in.science_7 + need_for_cognition + 
                  interpersonal.trust_1,
             data = results))
```

Trust in science, need for cognition, and interpersonal trust on trust in Vis
```{r}
results %>%
  gather(key = variables, value = values, 
         trust.in.science_7, need_for_cognition, interpersonal.trust_1) %>%
  ggplot(aes(x = values, y = vis.trust_6, color = variables)) +

  facet_grid(cols = vars(variables)) +
    geom_jitter() +
  geom_smooth(color = "black") +
  geom_blank() + 
   theme_minimal() +
  theme(panel.spacing = unit(2, "lines"))
```






Trust in Data

```{r}
results %>%
  ggplot(aes(x = data.trust_6, y = isCovidData, colour = as.factor(isCovidData))) +
  geom_jitter(data = results, width = 0.5) +
  # labs(title = "Trust in data") + 
  geom_vline(data = results %>% 
                group_by(complexity, isCovidData, chartType) %>%
                summarize(n = n(), 
                          data.trust_6 = mean(data.trust_6)), 
              aes(xintercept = data.trust_6, colour = as.factor(isCovidData))) +
  facet_grid(rows = vars(complexity), cols = vars(chartType)) +
  theme_minimal()

results %>% 
  group_by(complexity, isCovidData) %>%
  summarize(n = n(), 
            mean = mean(data.trust_6),
            se = sd(data.trust_6)/sqrt(n),
            n = n)
```

```{r}
model <- lm(formula = data.trust_6 ~ complexity * as.factor(isCovidData) * chartType
                                    + Age + Gender + State_1 + Education + Parents_education + Language + Ethnicity + Income + Religion + trust.in.science_7 + need_for_cognition + interpersonal.trust_1 ,
            data = results)
anova(model)

# post-hoc tests
aov(data.trust_6 ~ complexity * as.factor(isCovidData), data = results) %>% tukey_hsd()
aov(data.trust_6 ~ chartType * as.factor(isCovidData), data = results) %>% tukey_hsd()
# effect sizes
eta_squared(aov(data.trust_6 ~ complexity * as.factor(isCovidData) * chartType + 
                  Age + Gender + State_1 + Education + Parents_education + Language + 
                  Ethnicity + Income + Religion + trust.in.science_7 + need_for_cognition + 
                  interpersonal.trust_1,
             data = results))
emmeans(aov(data.trust_6 ~ complexity , data = results) , ~ complexity)
```

Trust in science, need for cognition, and interpersonal trust on trust in Data
```{r}
results %>%
  gather(key = variables, value = values, 
         trust.in.science_7, need_for_cognition, interpersonal.trust_1) %>%
  ggplot(aes(x = values, y = data.trust_6, color = variables)) +

  facet_grid(cols = vars(variables)) +
    geom_jitter() +
  geom_smooth(color = "black") +
  geom_blank() + 
   theme_minimal() +
  theme(panel.spacing = unit(2, "lines"))
```


















```{r}
results_long_data <- results %>%
  select(data.trust_1, data.trust_2, data.trust_3,
         data.trust_4, data.trust_5, data.trust_6,
         ResponseId, complexity,
         vlat_simple, vlat_moderate, vlat_complex) %>%
  gather(key = trustItemData, value = trustRatingData, 
         data.trust_1, data.trust_2, data.trust_3, data.trust_4, data.trust_5, data.trust_6)

results_long_data %>%
  ggplot(aes(x = trustRatingData, y = 1, color = complexity)) +
  geom_jitter() +
  ylim(0, 2) + 
  labs(title = "Trust in data (All)") + 
  geom_vline(data = results_long_data %>% 
               group_by(complexity, trustItemData) %>%
               summarize(n = n(), 
                         average = mean(trustRatingData)), 
             aes(xintercept = average, color = complexity)) +
  facet_grid(vars(trustItemData)) +
  theme_minimal()
```


# Relationship between trust in data and vis, across complexity

```{r}
results_long_data <- results %>%
  select(data.trust_1, data.trust_2, data.trust_3,
         data.trust_4, data.trust_5, data.trust_6,
         ResponseId, complexity,
         chartType, isCovidData, 
         vlat_simple, vlat_moderate, vlat_complex) %>%
  gather(key = trustItemData, value = trustRatingData, 
         # data.trust_1, data.trust_2, data.trust_3, data.trust_4, data.trust_5, 
         data.trust_6)

results_long_vis <- results %>%
  gather(key = trustItemVis, value = trustRatingVis, 
         # vis.trust_1, vis.trust_2, vis.trust_3, vis.trust_4, vis.trust_5, 
         vis.trust_6)

results_long_all <- merge(results_long_vis, results_long_data, 
                          by = c("ResponseId", "complexity", "chartType", "isCovidData"))

model<- glm(trustRatingVis ~  trustRatingData * complexity + 
              trustRatingData *  chartType + 
              trustRatingData *  as.factor(isCovidData),
                      data = results_long_all)
Anova(model)
```

```{r}
results_long_all %>%
  # filter(trustItemVis == "bar.vis_2") %>%
  ggplot(aes(x = trustRatingVis, y = trustRatingData, color = as.factor(isCovidData))) +
  geom_jitter(alpha = 0.25) +
  stat_smooth(method = "lm",
              formula = y ~ x,
              geom = "smooth", color = "black") +
  labs(title = "Relationship bewteen trust in Vis and Data") + 
  facet_grid(rows = vars(chartType), cols = vars(complexity)) +
  theme_minimal()
```


















# Does the trust items predict trust?


```{r}
model <- lm(formula = vis.trust_6 ~ vis.trust_1 * as.factor(isCovidData) + 
              vis.trust_2 * as.factor(isCovidData) + 
              vis.trust_3 * as.factor(isCovidData) + 
              vis.trust_4 * as.factor(isCovidData) + 
              vis.trust_5 * as.factor(isCovidData) + 
              Age + Gender + State_1 + Education + Parents_education + Language + 
              Ethnicity + Income + Religion + trust.in.science_7 + 
              need_for_cognition + interpersonal.trust_1,
            data = results)
anova(model)
summary(model)

# 4 and 5 has to do with whether the vis is actionable. Would it be used in daily life? Really depends on the topic - crop stuff might not be relevant. Need to account for the topic!!!!! Add "isCovidData" to model. 
```

```{r}
model <- lm(formula = data.trust_6 ~ data.trust_1 * as.factor(isCovidData) + 
              data.trust_2 * as.factor(isCovidData) + 
              data.trust_3 * as.factor(isCovidData) + 
              data.trust_4 * as.factor(isCovidData) + 
              data.trust_5 * as.factor(isCovidData) +
              Age + Gender + State_1 + Education + Parents_education + Language + 
              Ethnicity + Income + Religion + trust.in.science_7 + 
              need_for_cognition + interpersonal.trust_1,
            data = results)
summary(model)
anova(model)
```

```{r}
results %>%
  ggplot(aes(x = data.trust_1, y = data.trust_6, color = as.factor(isCovidData))) +
  geom_jitter() +
  geom_smooth(method="lm") +
  facet_wrap(~isCovidData) +
  theme_minimal()
```









How does performance on VLAT questions predict trust?

```{r}
model <- lm(formula = vis.trust_6 ~ vlat_simple * vlat_moderate * vlat_complex +
              Age + Gender + State_1 + Education + Parents_education + Language + 
              Ethnicity + Income + Religion + trust.in.science_7 + 
              need_for_cognition + interpersonal.trust_1,
            data = results)
anova(model)

emmeans(aov(vis.trust_6 ~ vlat_simple * vlat_complex , data = results) , ~ vlat_simple | vlat_complex)
```

```{r}
results %>%
  gather(key = vlat_level, value = vlat_performance, vlat_simple,  vlat_moderate, vlat_complex) %>%
  ggplot(aes(x = vis.trust_6, y = vlat_performance, colour = as.factor(assigned_vlat))) +
  geom_jitter(width = 0.5) +
  # y(0, 2) + 
  # labs(title = "Trust in data") + 
  # geom_vline(data = results %>% 
  #              group_by(complexity, isCovidData) %>%
  #              summarize(n = n(), 
  #                        vis.trust_6 = mean(vis.trust_6)), 
  #            aes(xintercept = vis.trust_6, colour = as.factor(isCovidData))) +
  facet_grid(rows = vars(vlat_level), cols = vars(chartType)) +
  theme_minimal() + 
  theme(panel.spacing = unit(2, "lines"))
        # legend.position = "none")
```


Overall distribution of VLAT performance

Trust in Vis 
```{r}
vlat_long <- results %>%
  gather(key = vlat_level, value = vlat_performance, vlat_simple,  vlat_moderate, vlat_complex) 

model <- lmer(formula = vlat_performance ~ vlat_level * isCovidData * chartType +
              Age + Gender + State_1 + Education + Parents_education + Language + 
              Ethnicity + Income + Religion + trust.in.science_7 + 
              need_for_cognition + interpersonal.trust_1 + (1|ResponseId),
            data = vlat_long)
Anova(model)

emmeans(aov(vlat_performance ~ vlat_level , data = results) , ~ vlat_simple | vlat_complex)

# post-hoc tests
aov(vlat_performance ~ vlat_level * as.factor(isCovidData), data = vlat_long) %>% tukey_hsd()
```

```{r}
results %>%
  gather(key = vlat_level, value = vlat_performance, vlat_simple,  vlat_moderate, vlat_complex) %>%
  group_by(vlat_level, chartType, isCovidData) %>%
  summarize(n = n(),
            mean_vlat_performance = mean(vlat_performance),
            se = sd(vlat_performance)/sqrt(n),
            n = n()) %>%
  ggplot(aes(x = vlat_level, y = mean_vlat_performance, 
             ymax = mean_vlat_performance + se, ymin = mean_vlat_performance - se,
             colour = vlat_level)) +
  geom_point() +
  geom_errorbar() +
  # labs(title = "Trust in data") + 
  # geom_vline(data = results %>% 
  #              group_by(complexity, isCovidData) %>%
  #              summarize(n = n(), 
  #                        vis.trust_6 = mean(vis.trust_6)), 
  #            aes(xintercept = vis.trust_6, colour = as.factor(isCovidData))) +
  facet_grid(rows = vars(isCovidData)) +
  theme_minimal() + 
  theme(panel.spacing = unit(2, "lines"))
        # legend.position = "none")
```


Trust in Data


```{r}
model <- lm(formula = data.trust_6 ~ vlat_simple * vlat_moderate * vlat_complex +
              Age + Gender + State_1 + Education + Parents_education + Language + 
              Ethnicity + Income + Religion + trust.in.science_7 + 
              need_for_cognition + interpersonal.trust_1,
            data = results)
anova(model)

emmeans(aov(data.trust_6 ~ vlat_simple * vlat_complex , data = results) , ~ vlat_simple | vlat_complex)
```









# How does provenance data predict trust?

Overall

```{r}
brushed <- results %>%
  gather(key = provenance_type, value = provenance_value, brushed, explore_interactions, explore_time) %>%
  group_by(provenance_type, chartType, isCovidData, complexity) %>%
  summarize(n = n(), 
            mean = mean(provenance_value), 
            se = sd(provenance_value)/sqrt(n),
            n = n) %>%
  filter(provenance_type == "brushed") %>%
  ggplot(aes(x = provenance_type, y = mean, ymax = mean + se, ymin = mean - se, color = as.factor(isCovidData))) +
  geom_point(position = position_dodge2(width = 0.5)) +
  geom_errorbar(width = 0.5, size = 0.66, position = "dodge") +
  facet_grid(rows = vars(complexity), cols = vars(isCovidData)) + 
  theme_minimal() +
  theme(panel.spacing = unit(2, "lines"))
brushed

interactions <- results %>%
  gather(key = provenance_type, value = provenance_value, brushed, explore_interactions, explore_time) %>%
  group_by(provenance_type, chartType, isCovidData, complexity) %>%
  summarize(n = n(), 
            mean = mean(provenance_value), 
            se = sd(provenance_value)/sqrt(n),
            n = n) %>%
  filter(provenance_type == "explore_interactions") %>%
  ggplot(aes(x = provenance_type, y = mean, ymax = mean + se, ymin = mean - se, color = as.factor(isCovidData))) +
  geom_point(position = position_dodge2(width = 0.5)) +
  geom_errorbar(width = 0.5, size = 0.66, position = "dodge") +
  facet_grid(rows = vars(complexity), cols = vars(chartType)) + 
  theme_minimal() +
  theme(panel.spacing = unit(2, "lines"))
interactions

exploreTime <- results %>%
  gather(key = provenance_type, value = provenance_value, brushed, explore_interactions, explore_time) %>%
  group_by(provenance_type, chartType, isCovidData, complexity) %>%
  summarize(n = n(), 
            mean = mean(provenance_value), 
            se = sd(provenance_value)/sqrt(n),
            n = n) %>%
  filter(provenance_type == "explore_time") %>%
  ggplot(aes(x = provenance_type, y = mean, ymax = mean + se, ymin = mean - se, color = as.factor(isCovidData))) +
  geom_point(position = position_dodge2(width = 0.5)) +
  geom_errorbar(width = 0.5, size = 0.66, position = "dodge") +
  facet_grid(rows = vars(chartType), cols = vars(complexity)) + 
  theme_minimal() +
  theme(panel.spacing = unit(2, "lines"))
exploreTime

exploreTime + interactions + brushed
ggsave("provenanceResults.png", width = 26, height = 14)
```
explore_interactions

```{r}
model <- lm(formula = explore_interactions ~ complexity * chartType * isCovidData +
              Age + Gender + State_1 + Education + Parents_education + Language + 
              Ethnicity + Income + Religion + trust.in.science_7 + 
              need_for_cognition + interpersonal.trust_1,
            data = results)
anova(model)
```

explore_time

```{r}
model <- lm(formula = explore_time ~ complexity * chartType * isCovidData +
              Age + Gender + State_1 + Education + Parents_education + Language + 
              Ethnicity + Income + Religion + trust.in.science_7 + 
              need_for_cognition + interpersonal.trust_1,
            data = results)
anova(model)
```



Hypothesis:
for the complex condition, we expect people who brushed more to have higher trust

```{r}
complexCondition <- results %>%
  filter(complexity == "complex")

# can change the predictor to bar.vis
model<- manova(cbind(data.trust_1, 
                     data.trust_2, 
                     data.trust_3, 
                     data.trust_4, 
                     data.trust_5, 
                     data.trust_6) ~ brushed + explore_interactions + explore_time, 
               data = complexCondition)
summary.aov(model)
```

Hypothesis:
for all the conditions, we expect people who hovered more to have higher trust


```{r}
# can change the predictor to bar.vis
model<- manova(cbind(vis.trust_6, 
                     vis.trust_5, 
                     vis.trust_4, 
                     vis.trust_3, 
                     vis.trust_2, 
                     vis.trust_1) ~ brushed + explore_interactions + explore_time, 
               data = results)
summary.aov(model)
```



# Affect on Trust {it's own section}

```{r}
results %>%
  gather(key = affects, value = affectRatings, affect.science_1,  affect.clarity_1, affect.aesthetic_1) %>%
  group_by(affects, chartType, isCovidData, complexity) %>%
  summarize(n = n(),
            mean = mean(affectRatings),
            se = sd(affectRatings)/sqrt(n),
            n = n()) %>%
  ggplot(aes(x = affects, y = mean, 
             ymax = mean + se, ymin = mean - se,
             colour = as.factor(isCovidData))) +
  geom_point(position = position_dodge2(width = 0.5)) +
  geom_errorbar(width = 0.5, size = 0.66, position = "dodge") +
  # labs(title = "Trust in data") + 
  # geom_vline(data = results %>% 
  #              group_by(complexity, isCovidData) %>%
  #              summarize(n = n(), 
  #                        vis.trust_6 = mean(vis.trust_6)), 
  #            aes(xintercept = vis.trust_6, colour = as.factor(isCovidData))) +
  facet_grid(rows = vars(chartType), cols = vars(complexity)) +
  theme_minimal() + 
  theme(panel.spacing = unit(2, "lines"))
        # legend.position = "none")
ggsave("affectMeasures.png", width = 17, height = 9)
```


```{r}
model <- lm(formula = affect.science_1 ~ complexity * chartType * isCovidData +
              Age + as.factor(Gender) + State_1 + Education + Parents_education + Language + 
              Ethnicity + Income + Religion + trust.in.science_7 + 
              need_for_cognition + interpersonal.trust_1,
            data = results)
anova(model)
```

```{r}
model <- lm(formula = affect.clarity_1 ~ complexity * chartType * isCovidData +
              Age + as.factor(Gender) + State_1 + Education + Parents_education + Language + 
              Ethnicity + Income + Religion + trust.in.science_7 + 
              need_for_cognition + interpersonal.trust_1,
            data = results)
anova(model)
summary(model)
```
```{r}
model <- lm(formula = affect.aesthetic_1 ~ complexity * chartType * isCovidData +
              Age + Gender + State_1 + Education + Parents_education + Language + 
              Ethnicity + Income + Religion + trust.in.science_7 + 
              need_for_cognition + interpersonal.trust_1,
            data = results)
anova(model)
summary(model)
```

Trust in Vis


```{r}
model <- lm(formula = vis.trust_6 ~ affect.science_1 * affect.clarity_1 * affect.aesthetic_1 +
              Age + Gender + State_1 + Education + Parents_education + Language + 
              Ethnicity + Income + Religion + trust.in.science_7 + 
              need_for_cognition + interpersonal.trust_1,
            data = results)
anova(model)

emmeans(aov(vis.trust_6 ~ affect.science_1 * affect.clarity_1 , data = results) , ~ affect.clarity_1)
```


Trust in Data

```{r}
model <- lm(formula = data.trust_6 ~ affect.science_1 * affect.clarity_1 * affect.aesthetic_1 +
              Age + Gender + State_1 + Education + Parents_education + Language + 
              Ethnicity + Income + Religion + trust.in.science_7 + 
              need_for_cognition + interpersonal.trust_1,
            data = results)
anova(model)

emmeans(aov(data.trust_6 ~ affect.science_1 * affect.clarity_1 , data = results) , ~ affect.clarity_1)
```










# Factor Analysis 


```{r}
factorAnalysis <- results %>%
  select(data.trust_1, data.trust_2, data.trust_3, data.trust_4, data.trust_5, data.trust_6,
         vis.trust_1, vis.trust_2, vis.trust_3, vis.trust_4, vis.trust_5, vis.trust_6,
         trust.in.science_1, trust.in.science_2, trust.in.science_3, trust.in.science_4, trust.in.science_5,
         trust.in.science_6, trust.in.science_7, trust.in.science_8, 
         cognition_1, cognition_2, cognition_3, cognition_4, cognition_5, cognition_6,
         # brushed, explore_interactions, # explore_time, 
         interpersonal.trust_1,
         vlat_simple, vlat_moderate, vlat_complex,
         # initial impression
         affect.science_1, affect.clarity_1, affect.aesthetic_1)

nfactors(factorAnalysis)
```

Factor 4 seem to have minimum compelxity, BIC is pretty low, and big jump for root mean
5 seems meh becuase of the big jump from 4-5 on complexity. 

```{r}
f7 <- fa(factorAnalysis, 7)
pdf(file = "f7.pdf",   # The directory you want to save the file in
    width = 15, # The width of the plot in inches
    height = 23) # The height of the plot in inches
fa.diagram(f7)
dev.off()
# based on the factor analysis, it looks like not all the vis Qs go together and not all the data Qs go together. 
```



